\TheTitle

### 2017-07-14 paper/study.tex
editing user opinions results

Among the 12 participants, there was nearly unanimous agreement that
for conceptual understanding and summarization tasks, \tool was easier
to work with than Gitk. The participants cited the ability to abstract
information about the merge from the clean summarization tables and
simple visualizations. Three participants suggested that someone with a
professional understanding of Gitk and the git command-line may be to
extract a conceptual understanding from the DAG and perform the
summarization tasks. One of these three participants said that they
would prefer to have both tools available, as they are able to
complement each other.

>>>>

Among the 12 participants, there was nearly unanimous agreement that for
conceptual understanding and summarization tasks; \tool was easier to
work with than Gitk. The participants cited the ability to abstract
information about the merge from the clean summarization tables and
simple visualizations. Three participants suggested that someone with a
professional understanding of Gitk and the git command-line may be to
extract a conceptual understanding from the DAG visualization and
perform the summarization tasks. One of these three participants said
that they would prefer to have both tools available, as they are able to
complement each other.
